---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# samplesizedev

<!-- badges: start -->
<!-- badges: end -->

The package samplesizedev performs unbiased sample size calculations for the development of risk models.

## Installation

You can install the development version of samplesizedev from [GitHub](https://github.com/) with:

``` r
# If package 'devtools is not installed, first install it'
# install.packages("devtools")
# require("devtools")

devtools::install_github("mpavlou/samplesizedev")
require(samplesizedev)
```

## Example

This is a basic example which shows how to:

a) to calculate the expected shrinkage and MAPE for a given sample size, and 

b) To calculate the sample size to achieve a target expected shrinkage of S=0.9 for a binary outcome

```{r example}
library(samplesizedev)

# Sample size=500; Prevalence=0.2; C-statistic=0.8; Number of predictors=10; 
# Calculate expected calibration slope and MAPE

expected_cs(n = 500, phi = 0.2, c = 0.85, p = 10, nsim = 1000)


# Target Calibration slope=0.9; Prevalence=0.2; c-statistic=0.8; Number of predictors=10; 
# Calculate sample size

samplesizedev(outcome="Binary", S = 0.9, phi = 0.2, c = 0.85, p= 10,  nsim = 1000)

```

