---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# samplesizedev

<!-- badges: start -->
<!-- badges: end -->

The package samplesizedev performs unbiased sample size calculations for the development of risk models.

## Installation

You can install the development version of samplesizedev from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mpavlou/samplesizedev")
```

## Example

This is a basic example which shows \n
a) how to calculate the expected shrinkage and MAPE for a given sample size, and \n
b) To calculate the sample size to achieve a taregt expected shrinkage of S=0.9

```{r example}
library(samplesizedev)

expected_cs(n = 530, p = 0.2, c = 0.85, n.predictors = 10, nsim = 1000, parallel = TRUE)

samplesizedev(outcome="Binary", S = 0.9, p = 0.2, c = 0.85, n.predictors = 10,  nsim = 1000)
```

